Kung Faux Pandas \\ \large Alternative Facts for Privacy Protection

### 2018-05-31 paper/main.tex
Auto Update from local Sharelatex

%\usepackage{nips_2017}
\usepackage[final]{nips_2017}
% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2017}

@@

\author{
  James King, Seth Russell, Tellen D. Bennett, Debashis Ghosh\\
  Data Science to Patient Value (D2V)\\
  School of Medicine \\
  University of Colorado Anschutz Medical Campus\\
  Aurora, CO\\
  \texttt{james.king@ucdenver.edu}, \texttt{seth.russell@ucdenver.edu},\\ \texttt{tell.bennett@ucdenver.edu} \texttt{debashis.ghosh@ucdenver.edu}
  }

@@

\begin{abstract}
A description of an end-to-end system for easily generating faux-data which is statistically similar to given real data but does not contain sensitive personal information.  This system makes enables data to be distributed for reproducibility testing and other purposes while in full compliance with HIPAA and GDPR.
\end{abstract}

@@

There is a large body of published literature detailing methods for overcoming this difficulty via ``anonymizing'' and ``synthesising'' data \cite{	patki_synthetic_2016, choi_generating_2017}, however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.

>>>>

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2018

% ready for submission
%\usepackage{nips_2018}

% to compile a preprint version, e.g., for submission to arXiv, add
% add the [preprint] option:
\usepackage[preprint]{nips_2018}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2018}

% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2018}

@@

\author{
  James King, Seth Russell, Tellen D. Bennett, Debashis Ghosh\\
  Data Science to Patient Value (D2V)\\
  School of Medicine\\
  University of Colorado Anschutz Medical Campus\\
  Aurora, CO\\
  \texttt{\{james.king, seth.russell, tell.bennett, debashis.ghosh\}@ucdenver.edu}
  }

@@

\begin{abstract}
A description of an end-to-end system for easily generating faux-data which is statistically similar to given real data but does not contain sensitive personal information.  This system, which is publicly available \footnote{\url{https://github.com/CUD2V/kungfauxpandas}}, enables data to be distributed for reproducibility testing and other purposes while in full compliance with HIPAA and GDPR.
\end{abstract}

@@

There is a large body of published literature detailing methods for overcoming this difficulty via ``anonymizing'' and ``synthesising'' data \cite{patki_synthetic_2016, choi_generating_2017}, however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
